Matching bullets

### 2015-11-20 imaging-paper.Rnw
Introduce the application

\section{Approach to automatic matching}
\hh{XXX all tentative}
Applying the  loess fit to a range of different surface cross cuts (see Figures~\ref{fig:manualmatch} and Figure~\ref{fig:manualmatch}, with cross cuts from 50 to 150) shows the striation marks across two bullets. Cross cuts of bullet 1 are shown on the left (cross cuts with values below 100) and cross cuts of bullets 2 are shown on the right (cross cuts with values above 100). A lot of the striation marks align, allowing for an easy visual assessment of the shared similarities between the two bullets.

@@

\includegraphics[width=\columnwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}\hh{Manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{images/matchup-rgl.png}
\caption{\label{fig:manualmatch}\hh{Different view of the manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}}
\end{figure}

>>>>

@@

\includegraphics[width=\columnwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}\hh{Manually adjusted side-by-side comparison of two lands from different bullets.}}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{images/matchup-rgl.png}
\caption{\label{fig:manualmatch}\hh{Different view of the manually adjusted side-by-side comparison of two lands from different bullets.}}
\end{figure}
